Fourmile Calibrations and Output

### 2025-12-14 params.Rmd
updating filepaths

combo <- read_csv('./38HRU_dec2024_updates/params_burn_unburn.csv') %>%
  mutate(burn = if_else(burn == "yes", "Burned", "Unburned"),
         input_data = if_else(input_data =='grid', 
                              'Gridded',
                              'Station'))

#write_csv(combo, './38HRU_dec2024_updates/params_burn_unburn.csv')
combo <- read_csv('./38HRU_dec2024_updates/params_burn_unburn.csv')

>>>>

combo <- read_csv('./38HRU_oct2025_updates/params_burn_unburn.csv') %>%
  mutate(burn = if_else(burn == "yes", "Burned", "Unburned"),
         input_data = if_else(input_data =='grid', 
                              'Gridded',
                              'Station'))

#write_csv(combo, './38HRU_oct2025_updates/params_burn_unburn.csv')
combo <- read_csv('./38HRU_oct2025_updates/params_burn_unburn.csv')
